Prey movement shapes the acquisition of predator expertise in a virtual bi-trophic system

### 2024-08-23 manuscript/manuscript.Rmd
update title to "acquisition"

---
title: "Prey movement shapes the development of predator expertise in a virtual bi-trophic system"
output: 
  word_document:
    reference_docx: manuscript-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: chicago-author-date.csl
---

>>>>

---
title: "Prey movement shapes the acquisition of predator expertise in a virtual bi-trophic system"
output: 
  word_document:
    reference_docx: manuscript-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: chicago-author-date.csl
---
